Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO--CC

### 2024-05-15 paper/manuscript.tex
correct small errors (esp. authors)

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,mask,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{cross-cultural psychology, social cognition, gaze following, individual differences, reliability\newline\indent Word count: XXX}
\usepackage{lineno}

@@

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Measuring variation in gaze-following across cultures, individuals, and age --- a showcase of the TANGO-CC},
  pdflang={en-EN},
  pdfkeywords={cross-cultural psychology, social cognition, gaze following, individual differences, reliability},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Measuring variation in gaze-following across cultures, individuals, and age --- a showcase of the TANGO-CC}
\author{Julia Prein (ORCID: 0000-0002-3154-6167)\textsuperscript{1,2}, Florian M. Bednarski (ORCID: 0000-0003-4384-4791)\textsuperscript{4}, Ardain Dzabatou\textsuperscript{5}, Michael C. Frank (ORCID: 0000-0002-7551-4378)\textsuperscript{6}, Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)\textsuperscript{4}, Josefine Kalbitz\textsuperscript{2}, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)\textsuperscript{7}, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)\textsuperscript{8}, Bahar Köymen (ORCID: 0000-0001-5126-8240)\textsuperscript{9}, Maira V. Manrique-Hernandez\textsuperscript{2}, Shirley Magazi (ORCID: 0009-0006-0479-9800)\textsuperscript{10}, Lizbeth Mújica-Manrique\textsuperscript{2}, Julia Ohlendorf\textsuperscript{2}, Damilola Olaoba\textsuperscript{2}, Wesley R. Pieters (ORCID:0000-0002-6152-249X)\textsuperscript{10}, Sarah Pope-Caldwell\textsuperscript{2}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,10}, Katie Slocombe (ORCID: 0000-0002-7310-1887)\textsuperscript{11}, Robert Z. Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{6}, Jahnavi Sunderarajan\textsuperscript{2}, Florence Tusiime\textsuperscript{3}, Wilson Vieira (ORCID: 0009-0001-9400-6328)\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{12}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{12}, Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)\textsuperscript{2,+}, \& Manuel Bohn (ORCID: 0000-0001-6006-1348)\textsuperscript{1,2,+}}
\date{}

\shorttitle{measuring gaze following across cultures}

@@

The authors made the following contributions. Julia Prein (ORCID: 0000-0002-3154-6167): Conceptualization, Methodology, Software, Investigation, Writing - Original Draft Preparation, Writing - Review \& Editing; Florian M. Bednarski (ORCID: 0000-0003-4384-4791): Investigation, Writing - Review \& Editing; Ardain Dzabatou: Investigation; Michael C. Frank (ORCID: 0000-0002-7551-4378): Investigation, Writing - Review \& Editing; Annette M. E. Henderson (ORCID: 0000-0003-4384-4791): Investigation, Writing - Review \& Editing; Josefine Kalbitz: Investigation, Writing - Review \& Editing; Patricia Kanngiesser (ORCID:0000-0003-1068-3725): Investigation, Writing - Review \& Editing; Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733): Investigation, Writing - Review \& Editing; Bahar Köymen (ORCID: 0000-0001-5126-8240): Investigation, Writing - Review \& Editing; Maira V. Manrique-Hernandez: Investigation; Shirley Magazi (ORCID: 0009-0006-0479-9800): Investigation; Lizbeth Mújica-Manrique: Investigation, Writing - Review \& Editing; Julia Ohlendorf: Investigation; Damilola Olaoba: Investigation; Wesley R. Pieters (ORCID:0000-0002-6152-249X): Investigation, Writing - Review \& Editing; Sarah Pope-Caldwell: Investigation; Roman Stengelin (ORCID: 0000-0003-2212-4613): Conceptualization, Methodology, Investigation, Writing - Review \& Editing; Katie Slocombe (ORCID: 0000-0002-7310-1887): Investigation, Writing - Review \& Editing; Robert Z. Sparks (ORCID: 0000-0001-7545-0522): Investigation; Jahnavi Sunderarajan: Investigation; Florence Tusiime: Investigation; Wilson Vieira (ORCID: 0009-0001-9400-6328): Investigation; Zhen Zhang (ORCID: 0000-0001-9300-0920): Investigation, Writing - Review \& Editing; Yufei Zong (ORCID: 0009-0000-5012-0244): Investigation; Daniel B. M. Haun (ORCID: 0000-0002-3262-645X): Conceptualization, Funding acquisition, Writing - Review \& Editing; Manuel Bohn (ORCID: 0000-0001-6006-1348): Conceptualization, Methodology, Writing - Review \& Editing.

Correspondence concerning this article should be addressed to Julia Prein (ORCID: 0000-0002-3154-6167), Universitätsallee 1, 21335 Lüneburg, Germany. E-mail: \href{mailto:manuel.bohn@leuphana.de}{\nolinkurl{manuel.bohn@leuphana.de}}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology\\\textsuperscript{3} Budongo Conservation Field Station\\\textsuperscript{4} School of Psychology, University of Auckland\\\textsuperscript{5} Université Marien Ngouabi\\\textsuperscript{6} Department of Psychology, Stanford University\\\textsuperscript{7} School of Psychology, University of Plymouth\\\textsuperscript{8} Department of Psychology, Koç University\\\textsuperscript{9} Division of Psychology, Communication, and Human Neuroscience, University of Manchester\\\textsuperscript{10} Department of Psychology and Social Work, University of Namibia\\\textsuperscript{11} Department of Psychology, University of York\\\textsuperscript{12} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences\\\textsuperscript{+} joint last author}

\abstract{%
Cross-cultural studies are crucial for establishing the universality and robustness of developmental milestones. Yet, suitable methods to measure variability in social cognition across linguistic and cultural settings are lacking. This paper describes the TANGO-CC (Task for Assessing Individual Differences in Gaze Understanding - Cross Cultural), a gaze-following task designed to measure imprecision in gaze following across individuals, ages, and communities. The development of the TANGO-CC involved two main phases: initial implementation and validation in Leipzig, Germany, followed by collaboration with cross-cultural researchers to expand the stimulus pool and collect data from 2.5- to 11-year-old children (N = 1377) from 17 diverse communities worldwide. The TANGO-CC captured individual differences and high internal consistency in each community. Within-community variation outweighed between-community variation. Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each cultural setting. We provide an open-source website for researchers to customize the task to their needs. Overall, the TANGO-CC represents a valuable contribution to the assessment of social-cognitive development in diverse social-cultural environments, facilitating future cross-cultural studies.
}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

More than a decade ago, Henrich et al. (2010) advocated for more diverse samples in psychological research and cautioned against relying solely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) backgrounds. Despite numerous calls for change, the subject pools reported in high-impact journals still lack diversity (Nielsen et al., 2017). This lack of representation creates inequities and hampers progress in theory building: If we want to draw inferences about the unique characteristics of human behavior and ``human nature'', we need to study it in many humans from many different backgrounds (Krys et al., 2024).

The present sampling bias might be especially problematic in research concerning the development of social cognition. Social cognition concerns the processes by which individuals encode and decode social information (Glynn \& Watkiss, 2016), which allows them to successfully participate in joint activities and communication. Many developmental theories emphasize the role of social interaction in the development of social cognition (e.g., reinforcement learning in gaze following; (Jasso \& Triesch, 2006)). However, social interactions differ substantially in their characteristics across communities and even across families and individuals. Cultural and social experiences influence the beliefs, values, norms and expectations of an individual, which, in turn, determines how they interpret other's actions. Consequently, Selcuk et al. (2023) have urged for studying how social-cultural factors on a macro-, community-level as well as a micro-, family-level influence the social cognition development.

Why are there not more social-cognitive studies focusing on the variation between diverse communities and individuals? A potential reason for the under-representation of these studies may be the scarcity of suitable tools (Bourdage et al., 2023). A suitable tool for studying individual- and community-level variation needs to address its (1) psychometric properties and (2) cross-cultural adaptations.

First, studies investigating variation between communities and/or individuals need to ensure that the captured variation is systematic and not just random noise. This requires measurement reliability and validity. Yet, social cognition studies based on US-American and European samples rarely report psychometric information (for a review, see Beaudoin et al., 2020). This picture further deteriorates when we pay attention to the reliability and validity of cross-cultural social cognition tasks (Bourdage et al., 2023; Hajdúk et al., 2020). It remains challenging to find reliable and valid tasks that can capture individual differences within one community, let alone finding tasks that can be applied across different cultural settings.

Second, adapting tasks to diverse cultural settings and re-assessing their validity and reliability might be especially important in the social-cognitive domain. If, in theory, stimuli used in social cognition tasks should depict people's everyday experiences, the tasks need to represent different social and cultural environments. Indeed, task performance can be diminished when stimuli are not adjusted (Peña, 2007). For example, Elfenbein and Ambady (2002) found better emotion recognition for members of the same national, ethnic, or regional group. Selcuk et al. (2023) concluded that children often attribute mental states more accurately and more frequently to individuals from the same cultural group. This underlines the importance of adapting tasks to each specific cultural context.

Broadly speaking, there are two different approaches that researchers can take to collect data that is comparable across cultural settings. One approach would be to translate the psychological construct into an individually designed study for each cultural setting. While this approach is most flexible and sensitive to cultural differences, it might be most feasible for studying up to a handful communities. Examples for studies that followed this approach are Mehta et al. (2011), Stengelin et al. (2020), Chasiotis et al. (2006). However, recent articles call for the inclusion of more field sites in cross-cultural studies (e.g., Krys et al., 2024). The approach of individually re-designing a study for each community might then become too demanding and time-consuming. Another approach would be to use the same standardized procedure across diverse cultural settings. This approach is less sensitive to each community's unique characteristics but allows for a direct comparison of data across cultural settings. Examples following this approach include Callaghan et al. (2011), Taumoepeau et al. (2019), Hughes et al. (2018), Hughes et al. (2014), Fujita et al. (2022). This paper aims to describe the development and psychometric properties of a standardized task that can be adapted to different social and linguistic settings.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\makeatletter
\usepackage{etoolbox}
\patchcmd{\maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{cross-cultural psychology, social cognition, gaze following, individual differences, reliability\newline\indent Word count: 5457}
\usepackage{lineno}

@@

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO--CC},
  pdfauthor={Julia Christin Prein (ORCID: 0000-0002-3154-6167)1,2, Florian M. Bednarski (ORCID: 0000-0003-4384-4791)4, Ardain Dzabatou5, Michael C. Frank (ORCID: 0000-0002-7551-4378)6, Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)4, Josefine Kalbitz2, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)7, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)8, Bahar Köymen (ORCID: 0000-0001-5126-8240)9, Maira V. Manrique-Hernandez2, Shirley Magazi (ORCID: 0009-0006-0479-9800)10, Lizbeth Mújica-Manrique2, Julia Ohlendorf2, Damilola Olaoba2, Wesley R. Pieters (ORCID:0000-0002-6152-249X)10, Sarah Pope-Caldwell2, Umay Sen (ORCID: 0000-0001-9488-0851)13, Katie Slocombe (ORCID: 0000-0002-7310-1887)11, Robert Z. Sparks (ORCID: 0000-0001-7545-0522)6, Roman Stengelin (ORCID: 0000-0003-2212-4613)2,10, Jahnavi Sunderarajan2, Kirsten Sutherland2, Florence Tusiime3, Wilson Vieira (ORCID: 0009-0001-9400-6328)2, Zhen Zhang (ORCID: 0000-0001-9300-0920)12, Yufei Zong (ORCID: 0009-0000-5012-0244)12, Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)2,+, \& Manuel Bohn (ORCID: 0000-0001-6006-1348)1,2,+},
  pdflang={en-EN},
  pdfkeywords={cross-cultural psychology, social cognition, gaze following, individual differences, reliability},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO--CC}
\author{Julia Christin Prein (ORCID: 0000-0002-3154-6167)\textsuperscript{1,2}, Florian M. Bednarski (ORCID: 0000-0003-4384-4791)\textsuperscript{4}, Ardain Dzabatou\textsuperscript{5}, Michael C. Frank (ORCID: 0000-0002-7551-4378)\textsuperscript{6}, Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)\textsuperscript{4}, Josefine Kalbitz\textsuperscript{2}, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)\textsuperscript{7}, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)\textsuperscript{8}, Bahar Köymen (ORCID: 0000-0001-5126-8240)\textsuperscript{9}, Maira V. Manrique-Hernandez\textsuperscript{2}, Shirley Magazi (ORCID: 0009-0006-0479-9800)\textsuperscript{10}, Lizbeth Mújica-Manrique\textsuperscript{2}, Julia Ohlendorf\textsuperscript{2}, Damilola Olaoba\textsuperscript{2}, Wesley R. Pieters (ORCID:0000-0002-6152-249X)\textsuperscript{10}, Sarah Pope-Caldwell\textsuperscript{2}, Umay Sen (ORCID: 0000-0001-9488-0851)\textsuperscript{13}, Katie Slocombe (ORCID: 0000-0002-7310-1887)\textsuperscript{11}, Robert Z. Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{6}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,10}, Jahnavi Sunderarajan\textsuperscript{2}, Kirsten Sutherland\textsuperscript{2}, Florence Tusiime\textsuperscript{3}, Wilson Vieira (ORCID: 0009-0001-9400-6328)\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{12}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{12}, Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)\textsuperscript{2,+}, \& Manuel Bohn (ORCID: 0000-0001-6006-1348)\textsuperscript{1,2,+}}
\date{}

\shorttitle{measuring gaze following across communities}

@@

The authors made the following contributions. Julia Christin Prein (ORCID: 0000-0002-3154-6167): Conceptualization, Methodology, Software, Formal Analysis, Resources, Writing - Original Draft Preparation, Writing - Review \& Editing; Florian M. Bednarski (ORCID: 0000-0003-4384-4791): Resources, Writing - Review \& Editing; Ardain Dzabatou: Resources, Writing - Review \& Editing; Michael C. Frank (ORCID: 0000-0002-7551-4378): Resources, Writing - Review \& Editing; Annette M. E. Henderson (ORCID: 0000-0003-4384-4791): Resources, Writing - Review \& Editing; Josefine Kalbitz: Resources, Writing - Review \& Editing; Patricia Kanngiesser (ORCID:0000-0003-1068-3725): Resources, Writing - Review \& Editing; Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733): Resources, Writing - Review \& Editing; Bahar Köymen (ORCID: 0000-0001-5126-8240): Resources, Writing - Review \& Editing; Maira V. Manrique-Hernandez: Resources, Writing - Review \& Editing; Shirley Magazi (ORCID: 0009-0006-0479-9800): Resources, Writing - Review \& Editing; Lizbeth Mújica-Manrique: Resources, Writing - Review \& Editing; Julia Ohlendorf: Resources, Writing - Review \& Editing; Damilola Olaoba: Resources, Writing - Review \& Editing; Wesley R. Pieters (ORCID:0000-0002-6152-249X): Resources, Writing - Review \& Editing; Sarah Pope-Caldwell: Resources, Writing - Review \& Editing; Umay Sen (ORCID: 0000-0001-9488-0851): Resources, Writing - Review \& Editing; Katie Slocombe (ORCID: 0000-0002-7310-1887): Resources, Writing - Review \& Editing; Robert Z. Sparks (ORCID: 0000-0001-7545-0522): Resources, Writing - Review \& Editing; Roman Stengelin (ORCID: 0000-0003-2212-4613): Resources, Writing - Review \& Editing; Jahnavi Sunderarajan: Resources, Writing - Review \& Editing; Kirsten Sutherland: Resources, Writing - Review \& Editing; Florence Tusiime: Resources, Writing - Review \& Editing; Wilson Vieira (ORCID: 0009-0001-9400-6328): Resources, Writing - Review \& Editing; Zhen Zhang (ORCID: 0000-0001-9300-0920): Resources, Writing - Review \& Editing; Yufei Zong (ORCID: 0009-0000-5012-0244): Resources, Writing - Review \& Editing; Daniel B. M. Haun (ORCID: 0000-0002-3262-645X): Funding acquisition, Writing - Review \& Editing; Manuel Bohn (ORCID: 0000-0001-6006-1348): Conceptualization, Methodology, Writing - Review \& Editing.

Correspondence concerning this article should be addressed to Julia Christin Prein (ORCID: 0000-0002-3154-6167), Universitätsallee 1, 21335 Lüneburg, Germany. E-mail: \href{mailto:julia.prein@leuphana.de}{\nolinkurl{julia.prein@leuphana.de}}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology\\\textsuperscript{3} Budongo Conservation Field Station\\\textsuperscript{4} School of Psychology, University of Auckland\\\textsuperscript{5} Université Marien Ngouabi\\\textsuperscript{6} Department of Psychology, Stanford University\\\textsuperscript{7} School of Psychology, University of Plymouth\\\textsuperscript{8} Department of Psychology, Koç University\\\textsuperscript{9} Division of Psychology, Communication, and Human Neuroscience, University of Manchester\\\textsuperscript{10} Department of Psychology and Social Work, University of Namibia\\\textsuperscript{11} Department of Psychology, University of York\\\textsuperscript{12} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences\\\textsuperscript{13} Department of Psychology, Developmental Psychology, Uppsala University\\\textsuperscript{+} joint last author}

\abstract{%
Cross-cultural studies are crucial for investigating the universality and robustness of cognitive developmental processes. Yet, suitable methods to measure variability in cognition across languages and communities are lacking. This paper describes the TANGO--CC (Task for Assessing Individual Differences in Gaze Understanding -- Cross-Cultural), a gaze following task designed to measure basic social cognition across individuals, ages, and communities. The TANGO--CC was developed and psychometrically assessed in one setting and subsequently adapted for cross-cultural data collection. Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each community. The TANGO--CC captured individual differences and showed good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities. Within-community variation outweighed between-community variation. We provide an open-source website for researchers to customize and use the task. The TANGO--CC represents a valuable contribution to assessing basic social cognition in diverse communities, establishing a roadmap for researching cross-cultural individual differences.
}

@@

\section{Introduction}\label{introduction}

For decades, researchers have advocated for more diverse samples in psychological research and cautioned against relying solely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) communities (Henrich et al., 2010; Lillard, 1998).
Despite numerous calls for change, the subject pools reported in high-impact journals still lack diversity (Gutchess \& Rajaram, 2023; Nielsen et al., 2017).
This lack of representation hinders progress in theory building: inferences about the universal and variable aspects of the human cognitive system cannot be drawn from data collected in single communities (Krys et al., 2024).

One reason for the lack of diversity in psychological studies is the scarcity of suitable methods to collect comparable psychological data in different communities (Bourdage et al., 2023). This shortage of suitable measures is even more prevalent in developmental psychology. In this paper, we describe the construction and psychometric evaluation of a measure of basic social cognition (gaze following) in children as a concrete example for how to overcome this problem.

Studies investigating variation between communities and/or individuals need to ensure that the captured variation is systematic and not just random noise: measures need to be reliable and valid.
This, of course, applies to all fields of psychology. Given the topic of this paper, we will focus on measures of social cognition for children. Studies on social cognition based on US-American and European samples rarely report psychometric information (for a review, see Beaudoin et al., 2020).
This picture further deteriorates when we look at cross-cultural social cognition tasks (Bourdage et al., 2023; Hajdúk et al., 2020; Waschl \& Chen, 2022).
Thus, it is already challenging to find reliable and valid tasks that can capture individual differences within one community, let alone tasks that do so across different communities.

Adapting tasks to diverse communities and re-assessing their validity and reliability might be especially important in the social-cognitive domain.
If, in theory, stimuli used in social cognition tasks should relate to people's everyday experiences, the tasks need to represent different communities.
Indeed, task performance can be diminished when stimuli are not adjusted (Peña, 2007).
For example, Elfenbein and Ambady (2002) found better emotion recognition for members of the same national, ethnic, or regional group.
Selcuk et al. (2023) concluded that children often attribute mental states more accurately and more frequently to individuals from the same community.
This underlines the importance of adapting tasks to each specific cultural context.

Broadly speaking, there are two different approaches that researchers can take to collect cross-cultural data.
One approach would be to translate the psychological construct into an individually designed study for each community (termed ``assembly''; He and Vijver (2012), Waschl and Chen (2022)).
While this approach is most flexible and sensitive to cultural differences, it might be most feasible for studying up to a handful of communities as it becomes too demanding and time-consuming.
Most importantly, this approach assumes that the measured underlying concept is the same, while absolute task scores are not comparable across the communities.
Another approach would be to use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of culturally inappropriate stimuli (termed ``adoption'' and ``adaptation'', respectively; He and Vijver (2012), Waschl and Chen (2022)).
This approach is less sensitive to each community's unique characteristics but allows for a direct comparison of the data across communities.
Examples following this approach include Callaghan et al. (2011), Taumoepeau et al. (2019), Hughes et al. (2018), Hughes et al. (2014), Fujita et al. (2022), Mehta et al. (2011), Stengelin et al. (2020), and Chasiotis et al. (2006).
The present paper aims to describe the development and psychometric properties of a standardized task that can be adapted to diverse communities.

The task presented here focuses on gaze following, that is, the ability to identify the attentional focus of another agent.
Gaze following develops early in infancy (Del Bianco et al., 2019; Tang et al., 2024) and contributes to social learning, communication, and collaboration (Bohn \& Köymen, 2018; Hernik \& Broesch, 2019; Shepherd, 2010; Tomasello et al., 2007).
While gaze following is one of the most fundamental social-cognitive abilities, studies focusing on cultural variations are rare.
The few existing results are mixed on whether gaze following is influenced by cultural factors or not (Callaghan et al., 2011; Hernik \& Broesch, 2019).

The task presented here builds upon the TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open) by Prein et al. (2023).
The TANGO measures participants' imprecision in locating an agent's attentional focus.
It has been shown to reliably capture individual differences in a German child sample and an English-speaking remote adult sample.
The task was sensitive to developmental changes and linked to children's receptive vocabulary.
Furthermore, an exploratory analysis showed that children performed equally well in a task version with animal faces compared to cartoon human faces (Prein et al., 2024).
This suggests that superficial variations in the stimulus design do not influence children's performance in the task.
